---
title: "3D Visualization and Prediction Spine Fractures"
author: "Jiayuan Shi"
date: "Feb.18, 2016"
output: pdf_document
---

```{r, message=FALSE, warning=FALSE}
flexion_data <- read.csv("Flexion.csv",header = T)
union_data <- read.csv("uni.csv",header = T)
names(flexion_data)
flexion.difference <- matrix(rep(0,279216),nrow=2493)
i <- 1
j <- 1
flexion.mean <- NULL
flexion.se <- NULL
while (i < 225) {
  flexion.difference[,j] <- flexion_data[,i]-flexion_data[,i+1]
  flexion.mean[j] <- mean(flexion.difference[,j],na.rm = T)
  flexion.se[j] <- sum((flexion.difference[,j])^2,na.rm = T)
  i <- i+2
  j <- j+1
}  
flexion.mean # mean difference for Flexion group
flexion.se # squared error for Flexion group

union.difference <- matrix(rep(0,320096),nrow=2858)
i <- 1
j <- 1
union.mean <- NULL
union.se <- NULL
while (i < 225) {
  union.difference[,j] <- union_data[,i]-union_data[,i+1]
  union.mean[j] <- mean(union.difference[,j],na.rm = T)
  union.se[j] <- sum((union.difference[,j])^2,na.rm = T)
  i <- i+2
  j <- j+1
}  
union.mean # mean difference for Union group
union.se # squared error for Union group
```

In order to examine whether the types and methods have influence on mean difference and squared error between the experimental and simulation results, we conduct two-way ANOVA.

For Flexion group, we firstly constructed two matrices. They are,  
$flexion.data.mean$ with three columns: its type, method and mean difference;   $flexion.data.se$ with three columns: its type, method and squared error.
```{r, message=FALSE, warning=FALSE}
flexion.type <- c(rep(c(rep("CF",4),rep("vM",4)), 14))
flexion.method <- c(rep(c("Idealized","Experimental","Specific","Generic"),28))
# Flexion matrices
flexion.data.mean <- cbind(flexion.type, flexion.method, flexion.mean )
flexion.data.se <- cbind(flexion.type, flexion.method, flexion.se)
```

Next, we used two-way ANOVA procedure to conduct a hypothesis tests to check if the Flexion type, method and their interactions have significant influence on the mean difference or squared error. 
```{r, message=FALSE, warning=FALSE}
# Influence of Flexion types and methods on mean difference
flexion.mean.fit <- aov(flexion.mean ~ flexion.type*flexion.method)
summary(flexion.mean.fit) 
```
The p-value of $flexion.type$ is 0.00147, which indicates a significant influence of Flexion type on its mean difference. Similarly, the p-value of $flexion.method$ is 0.02657, which indicates a significant influence of Flexion method on its mean difference. 

```{r, message=FALSE, warning=FALSE}                    
# Influence of Flexion types and methods on squared error
flexion.se.fit <- aov(flexion.se ~ flexion.type*flexion.method)
summary(flexion.se.fit)
```                          
The p-value of $flexion.type$ is 0.0259, which indicates a significant influence of  Flexion type on its squared error. 

For Union group, we also firstly constructed two matrices. They are,  
$union.data.mean$ with three columns: its type, method and mean difference;   $union.data.se$ with three columns: its type, method and squared error.
```{r, message=FALSE, warning=FALSE}  
type.union <- c(rep(c(rep("CF",4),rep("vM",4)), 14))
union.method <- c(rep(c("Idealized","Experimental","Specific","Generic"),28))
# Union matrices
union.data.mean <- cbind(type.union, union.method, union.mean )
union.data.se <- cbind(type.union, union.method, union.se )
```

Next, we used two-way ANOVA procedure to conduct a hypothesis tests to check if the Union type, method and their interactions have significant influence on the mean difference or squared error. 
```{r, message=FALSE, warning=FALSE} 
# Influence of Union types and methods on mean difference
union.mean.fit <- aov(union.mean ~ type.union*union.method)
summary(union.mean.fit)
```
All the p-values are larger than 0.05, which indicates non-significant influence of any Union factors on its mean difference. 
           
```{r, message=FALSE, warning=FALSE} 
# Influence of Union types and methods on squared error
union.se.fit <- aov(union.se ~ type.union*union.method)
summary(union.se.fit)
````
All the p-values are larger than 0.05, which indicates non-significant influence of any Union factors on its mean difference. 